Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-03-04 size_differentiated_export.tex
Updates from Overleaf

%FIG7
 \begin{figure}[ht]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export}
	\caption{Amount of biomass exported in normalized units by each sinking velocity class in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for three different Junge slopes: $\xi =$ 4 (top), $\xi =$ 3 (middle), and $\xi =$ 2 (bottom; see Figure \ref{fig: sinking_velocity_spectrum}). Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}. \fixme{show only 3 ws?}}
	\label{fig: biomass_export_remin}
\end{figure}

>>>>

%FIG7
 \begin{figure}[ht]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi =4$. Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
	\label{fig: biomass_export_remin}
\end{figure}
